TR Invariant T.I.

### 2017-03-29 Notes of various papers/TR invariant topological insulators T. Hughes. Dissertation/note.tex
[minor] Update something about spin-waves in this model...

@@

    \subsection{Numerical result}
    \label{sec:Numerical result}
    \textbf{Note}: Results in this section are contained in the file
    "Lattice Dirac Model (2+1)-d.nb", and the file
    "Dirac\_Lattice\_Model\_21\_d.m".

@@

    It is found that at $m=-2$, there is a band crossing at $p_x=0$:
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.6\linewidth]{pics/N6m-2.pdf}
        \caption{The Eigenvalue plot for $m=-2$. Plotted as
        $E_{p_x}$v $p_x$ }
    \end{figure}

    Also, at $m=2$, there is a band crossing at $p=\pm\pi$:
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.6\linewidth]{pics/N6m2.pdf}
        \caption{The Eigenvalue plot for $m=2$. Plotted as
        $E_{p_x}$v$p_x$ }
    \end{figure}

    Since the paper will be focusing in points around $p_x=0$, I will
    focus in $m=-2$. In this case, I want to find more information
    about the eigenvectors.

@@

    \subsection{Discussion about the Lattice Model}
    \label{sec:DisAboutLatticeModel}
    I notice that equation (2.19) transformed according to (2.20)
    is not exactly equation (2.21), but is:
    \begin{align}
        &H =\sum_{p_x,p_y} c^\dagger_{p_x,p_y}\times
        \nonumber\\
        &
        \left[
            2\sin(p_x)\sigma^x + 2\sin(p_y)\sigma^y
            +(2-m-2\cos(p_x)-2\cos(p_y))\sigma^z
        \right] c_{p_x,p_y}
    \end{align}
    This result does not become the continuum Dirac Hamiltonian as
    $p_x,p_y$ goes to zero. Therefore, I suspect that certain
    constants should be modified so that:

    And the result is similar to previous study, except that the band
    crossing happens at different values of $m$. For example, the
    eigenvalue of original and the modified equation (2.21) are
    plotted in Mathematica notebook "Eq2.21-Demo.nb". Also, the
    solution to the infinite cylinder boundary condition has again two
    band crossings, each at $(m,p_x)$ equals $(0,0)$ and $(2,\pm\pi)$
    (for $N=3$ case).

>>>>

\subsection{Numerical Solution in Infinity Cylinder Geometry}
\label{sec:Numerical Solution in Infinity Cylinder Geometry}

@@

\textbf{Note}: Numerical calculations in this section are contained in the file
"Lattice Dirac Model (2+1)-d.nb", and the file
"Dirac\_Lattice\_Model\_21\_d.m".

@@

It is found that at $m=-2$, there is a band crossing at $p_x=0$:
\begin{figure}[H]
    \centering
    \includegraphics[width=0.2\linewidth]{pics/N6m-2.pdf}
    \caption{The Eigenvalue plot for $m=-2$. Plotted as
    $E_{p_x}$-$p_x$ }
\end{figure}

Also, at $m=2$, there is a band crossing at $p=\pm\pi$:
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/N6m2.pdf}
    \caption{The Eigenvalue plot for $m=2$. Plotted as
    $E_{p_x}$-$p_x$ }
\end{figure}

When the band crosses, there will be two eigenvectors, corresponds to
the two crossed bands, in the form of:
\begin{align}
    \psi_{p_x} &= \left(\vphantom{\frac12}\psi(p_x),1,\psi(p_x),1,\psi(p_x),1\right)^T \\
    \phi_{p_x} &= \left(\vphantom{\frac12}\phi(p_x),1,\phi(p_x),1,\phi(p_x),1\right)^T
\end{align}
where $\psi(p_x)$ and $\phi(p_x)$ are functions of $p_x$. A look into
the plot of $\psi(p_x)$ and $\phi(p_x)$ reveals that they together
provide the path way for excited particles to transfer from the lower
band to the upper band.
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/upperSpinWaveMN2.pdf}
    \caption{Plot of $\psi(p_x)$ and $\phi(p_x)$ when $m=-2$}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/upperSpinWaveM2.pdf}
    \caption{Plot of $\psi(p_x)$ and $\phi(p_x)$ when $m=2$, where I
    have extended the range s.t. $p_x\in\{-\pi,3\pi\}$ to make the
    meaning clear.}
\end{figure}

Therefore, one may predict a pure spin-up wave transfering in the
point $p_x=0$ when $m=2$, and $p_x=\pm\pi$ when $m=2$.

    \subsection{Why I think the Lattice Model is wrong}

    I notice that equation (2.19) transformed according to (2.20)
    is not exactly equation (2.21), but is:
    \begin{align}
        &H =\sum_{p_x,p_y} c^\dagger_{p_x,p_y}\times
        \nonumber\\
        &
        \left[
            2\sin(p_x)\sigma^x + 2\sin(p_y)\sigma^y
            +(2-m-2\cos(p_x)-2\cos(p_y))\sigma^z
        \right] c_{p_x,p_y}
    \end{align}
    This result does not become the continuum Dirac Hamiltonian as
    $p_x,p_y$ goes to zero. Therefore, I suspect that certain
    constants should be modified so that:

    The calculated result is similar to that in the previous section,
    except that the band crossing happens at different values of $m$.
    \footnote{For example, the eigenvalue of original and the modified equation
    (2.21) are plotted in Mathematica notebook "Eq2.21-Demo.nb". Also,
    the solution to the infinite cylinder boundary condition has again
    two band crossings, each at $(m,p_x)$ equals $(0,0)$ and
    $(2,\pm\pi)$ (for $N=3$ case).}
    So the essential point is unaltered by the difference in some
    constants. However, in the correct calculation, the crossing band
    appears at $m=0$, which represents a massless spin-$\frac{1}{2}$
    particle. I think this should have some theoretical implications.

\subsection{Calculation Note unrelated to the main-subject}

Since the paper will be focusing in points around $p_x=0$, I focused
in $m=-2$ at first. In this case, I want to find more information
about the eigenvectors.

@@
